Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2022-03-24 reports/manuscript.Rmd
Fix descriptive table

documentclass     : "apa6"
classoption       : "man"
csl               : vancouver-brackets-meta.csl
output:papaja::apa6_pdf
nocite            : "`r params$nocite_list`"
---

@@

```{r desctable, eval = TRUE, results="asis"}
reviews_tables[[1]]$table
```

>>>>

documentclass     : "apa6"
classoption       : "man"
csl               : vancouver-brackets-meta.csl
output            : papaja::apa6_pdf
header-includes:
    - \usepackage{makecell}
    - \usepackage{booktabs}
    - \usepackage{colortbl}
# nocite            : "`r # params$nocite_list`"
---

@@

```{r desctable, eval = TRUE, results="asis"}
reviews_tables$kable$table %>%
    kableExtra::row_spec(1:reviews_tables$kable$nrow, hline_after = TRUE) %>%
    kableExtra::row_spec(0, bold = TRUE) %>%
    kableExtra::column_spec(3:4, width = "2cm") %>%
    kableExtra::column_spec(5, width = "1.5cm") %>%
    kableExtra::column_spec(6:8, width = "3cm") %>%
    kableExtra::kable_styling(
        latex_options = c("repeat_header"),
        font_size = 5
    ) %>%
    kableExtra::landscape()
```
